Hierarchical Time Series Forecasting in Emergency Medical Services

### 2022-11-18 manuscript/05-results.qmd
typo

In this section, we compare the forecasting performance of Naive, ETS, GLM, Tscount and the ensemble model using base forecast and Minimum Trace (Mint) methods. We have also computed the forecast accuracy for Ordinary Least Square (OLS) and Weighted Least Square (WLS) approaches. However, they are not reported here because their accuracy is outperformed by Mint. We should also note that forecasts, and consequently their corresponding errors, are generated for the entire hierarchy and they could be reported at any level, if required.

>>>>

In this section, we compare the forecasting performance of Naive, ETS, Poisson regression using GLM, Poisson regression with serial correlations using tscount and the ensemble model using base forecast and Minimum Trace (Mint) methods. We have also computed the forecast accuracy for Bottom-up (BU), Ordinary Least Square (OLS) and Weighted Least Square (WLS) approaches. However, they are not reported here because their accuracy is outperformed by Mint. We should also note that forecasts, and consequently their corresponding errors, are generated for the entire hierarchy and they could be reported at any level, if required.
